Universal Anonymous Signatures

### 2022-08-16 prism-backend/research/gsac/app-uas-proofs.tex
Added proof sketch for interactive variant.

>>>>

\subsection{Security of $\CUASGen^{int}$}
\label{sapp:sec-interactive}

\paragraph{Issuance Anonymity.} Since issuance anonymity is independent of
whether signature/authentication is interactive or not, the proof for issuance
anonymity in $\CUASGen^{int}$ is the same as for \CUASGen.

\paragraph{Signature Anonymity.} To see why the interactive variant has
signature anonymity, assume an adversary \adv~that breaks it. We build \advB
against the non-interactive \ExpSigAnonb from \adv~as follows. \advB initializes
everything as in the \ExpSigAnonb game. When \adv~initiates a call to its
interactive \SIGN (resp. \CHALb) oracle, \advB forwards it to its own oracle
(but concatenating the random number to the message to be signed). \advB
forwards the response from its oracle to \adv. After such simulation, \advB just
outputs whatever $\adv$ outputs. Clearly, the simulation is perfect and, if
\adv~wins with non-negligible probability in the interactive case, then so
does \advB in the non-interactive case. Specifically, note that, since the \Sign
algorithm is probabilistic, even if a malicious verifier picks the same random
number in several queries (to the same or different users), the result will be
indistinguishable with overwhelming probability.

\paragraph{Unforgeability and non-frameability.} The simulation described for
the anonymity case (i.e., \advB choosing the random numbers, and concatenating
them to the message to be signed by the oracle) applies here too. Since the
interactive protocol includes non-interactive proofs for the $\NIZKRel^{\Sign}$
and $\NIZKRel^{Open}$ relations, the proofs for unforgeability and
non-frameability of \CUASGen still apply.

### 2022-08-16 prism-backend/research/gsac/formal-uas.tex
Added proof sketch for interactive variant.

In this section, we give a generic construction of an \UAS scheme, based on
generic building blocks. We use three different NP relations in our generic
construction. Namely: $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and
$\NIZKRel_{\Open}$, described next and specified in CS notation \needcite
in \figref{fig:nizkrels}.

@@

\paragraph{Interactive Credential Presentations.}
\todo{Does this meet the model? If not, we should move this elsewhere.}
In \appref{app:interactive-uas}
we show how to convert the non-interactive signing and verification processes
into an interactive protocol. While the transformation is quite straightforward,
it is of high relevance for real world use cases.

>>>>

In this section, we give a generic construction of an \UAS scheme, based on
generic building blocks. We use three different NP relations in our generic
construction. Namely: $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and
$\NIZKRel_{\Open}$, described next and specified in CS notation \cite{cs97}
in \figref{fig:nizkrels}.

@@

\paragraph{$\CUASGen^{int}$: Interactive Credential Presentations with replay
  protection.}
%
In group signatures, signing and verification are non-interactive processes;
whereas in anonymous credentials, they are an interactive protocol. \CUASGen
targets the non-interactive approach. Now, we sketch how to transform this into
an interactive protocol that ensures replay protection.

Modelling-wise, this requires to replace the \Sign and \Verify functions with
a single $\langle 1/0,(\yeval,\utrans_{\Sig})/\bot \rangle \gets \langle
\Sign(\usk,\opk,\sCred,\msg,\feval), \Verify(\opk,\sipk,\msg,\feval) \rangle$,
where $\utrans_{\Sig}$ is the transcript of the protocol, and is logged now in
an equivalent of the \SIG table (\CSIG for challenge transcripts). The \SIGN
and \CHALb oracles now also accept a random value from the adversary, but
are otherwise adapted in the natural way, where the signer is always honest, but
the verifier is played by the adversary (e.g., similar to the \OBTAIN oracle).

The construction is also simple. Basically, prior to signing the message, we
require that the verifier sends to the user a number picked uniformly at random
from an appropriate domain, which must be concatenated to the signed message. If
there is no need to actually sign a message, then the message is set to an empty
string, and the user only signs the random number.
%
If the logic within the \feval and \finsp functions needs to ignore the random
value $rnd$ sent by the verifier, note that it is trivial to transform these
functions so that they treat the message concatenated with $rnd$ as a pair
$(\msg,rnd)$, and simply ignore $rnd$.

We sketch security of $\CUASGen^{int}$ in \appref{sapp:sec-interactive} assuming
the same security properties as in \UAS. Note that extra properties may be
needed in some scenarios. For instance, informally, the non-interactive version
does not provide deniability and, thus, our transform to the interactive case
does not provide it either. On the other hand, transferability is possible in
both cases, which may be useful, e.g., in situations where chaining multiple
requests is needed.
%
However, since probably the most common use of interactive presentations simply
worry about preventing replay attacks, we leave a more detailed analysis of
possible transforms (still meeting the \UAS model) out of scope.

### 2022-08-16 prism-backend/research/gsac/introduction-paper.tex
Added proof sketch for interactive variant.

Also, both AC and GS branches have experienced remarkable efforts towards
generalisation. In the AC domain, malleable signatures are used as core building
block in \cite{cklm14}, to allow building both conventional AC and Delegatable
AC systems, depending on the transformation supported by the malleable
signatures. In GS, very recently, BiAS \cite{lnpy21} and MPS \needcite~
flexibilize the trade-off between anonymity and accountability.

@@

\paragraph{Generic construction, and connections with previous schemes.} %
We give a generic construction based on well-known building blocks, and prove
its security. To prove its universality, we show how restrictions of our generic
construction directly imply the direct ancestors of UAS: group signatures and
anonymous credentials. This includes not only their vanilla versions, but also
relevant variants, such as MPS \needcite, (a modified version of) group
signatures with message-dependent opening \cite{seh+12}, or anonymous
credentials with revocation \cite{cks10}. We also show how minimal variations in
our generic construction allow us to build ring signatures \cite{rst06} or
delegatable anonymous credentials \cite{bcc+09}. The most interesting part being
that, while we prove implications with other previously known schemes, our
generalisation approach allows to merge features of them: e.g., one can easily
model and instantiate GSs with with no revocation at all, ACs with full
de-anonymization, or anything in between -- like being able to deanonymize only
if certain conditions are met.

>>>>

Also, both AC and GS branches have experienced remarkable efforts towards
generalisation. In the AC domain, malleable signatures are used as core building
block in \cite{cklm14}, to allow building both conventional AC and Delegatable
AC systems, depending on the transformation supported by the malleable
signatures. In GS, very recently, BiAS \cite{lnpy21} and MPS \cite{ngsy22}
flexibilize the trade-off between anonymity and accountability.

@@

\paragraph{Generic construction, and connections with previous schemes.} %
We give a generic construction based on well-known building blocks, and prove
its security. To prove its universality, we show how restrictions of our generic
construction directly imply the direct ancestors of UAS: group signatures and
anonymous credentials. This includes not only their vanilla versions, but also
relevant variants, such as MPS \cite{ngsy22}, (a modified version of) group
signatures with message-dependent opening \cite{seh+12}, or anonymous
credentials with revocation \cite{cks10}. We also show how minimal variations in
our generic construction allow us to build ring signatures \cite{rst06} or
delegatable anonymous credentials \cite{bcc+09}. The most interesting part being
that, while we prove implications with other previously known schemes, our
generalisation approach allows to merge features of them: e.g., one can easily
model and instantiate GSs with with no revocation at all, ACs with full
de-anonymization, or anything in between -- like being able to deanonymize only
if certain conditions are met.
